msprime 1.0: an efficient and extensible coalescent simulation framework

### 2020-02-24 paper.tex

We also support variable recombination rates along a chromosome.
This allows us to model both recombination hotspots like
\texttt{msHOT}~\citep{hellenthal2007mshot} and also empirical
recombination maps like those supported by X Y Z.
(What about ~\cite{wang2014new}?)
We have also implemented gene
conversion following the model defined by~\cite{wiuf2000coalescent}
and used in \ms. Further features are planned to model bacterial
evolution [Can you elaborate here please Franz?]

@@

\subsection*{Discrete time Wright-Fisher}
The coalescent is a good approximation for ancient history, but
is bad for the recent past and in particular when we have large
sample
sizes~\citep{wakeley2012gene,bhaskar2014distortion,nelson2020accounting}.
Describe basic
approach [DOM, can you fill in please].
See ~\cite{nelson2020accounting} for more details.
We compare the peformance of this simulation in Fig X
with ARGON~\citep{palamara2016argon}, a specialised DTWF simulator.

>>>>

We also support variable recombination rates along a chromosome.
This allows us to model both recombination hotspots like
\texttt{msHOT}~\citep{hellenthal2007mshot} and also empirical
recombination maps like those supported by X Y Z.
(What about ~\cite{wang2014new}?)
We have also implemented gene
conversion following the model defined by~\cite{wiuf2000coalescent}
and used in \ms. 
% % Uncomment this sentence, when the corresponding issue in the msprime github repo is resolved.
% Furthermore, msprime is now able to simulate gene conversion events that are 
% initiated proportional to the local recombination rate specified by the recombination map.

Gene conversion is particularly useful to model homologous recombination in bacterial evolution.
We compare the performance of \msprime\ with gene conversion to \ms\ and
the whole bacterial genome simulator SimBac~\citep{brown2016simbac}.
Further features are planned to model bacterial evolution. In particular, we
aim to include bacterial gene transfer and utilize the succinct tree sequence structure
to represent the resulting ancestral gene transfer graph~\citep{baumdicker2014AGTG}.

@@

\subsection*{Discrete time Wright-Fisher}
The coalescent is a good approximation for ancient history, but
is bad for the recent past and in particular when we have large
sample
sizes~\citep{wakeley2012gene,bhaskar2014distortion,nelson2020accounting}.
Describe basic
approach [DOM, can you fill in please].
See ~\cite{nelson2020accounting} for more details.
We compare the performance of this simulation in Fig X
with ARGON~\citep{palamara2016argon}, a specialised DTWF simulator.
